Normal States Training for High Accuracy Event Detection

### 2016-07-02 paper/ieeeFormat.tex
add 20newsgroups and their categories in wiki

\section{Experiments}
\begin{figure}
        \centering
        \includegraphics[height=4.0cm]{img/pmi.pdf}
        \caption{The quality of all twitter topics learned by NS-Prior-LDA increases with normal states weight (\(\lambda\)) before \(\lambda=12.8\). The optimized PMI is gained with moderate normal states weight when considering topics \(k\leq K_{\bm{KB}}\) and topics \(k > K_{\bm{KB}}\) together.}
\end{figure}

>>>>

\section{Experiments}
\subsection{Effects of Normal States Initialization}
We use 20newsgroups\cite{lang1995newsweeder} dataset\footnote{http://qwone.com/~jason/20Newsgroups} to check the effects of normal states initialization.
\begin{table}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|l|}
\hline
comp.graphics            & Category:Computer graphics      \\ \hline
comp.os.ms-windows.misc  & Category:Microsoft Windows      \\ \hline
comp.sys.ibm.pc.hardware & Category:IBM personal computers \\ \hline
comp.sys.mac.hardware    & Category:Macintosh computers    \\ \hline
comp.windows.x           & Category:X Window System        \\ \hline
rec.autos                & Category:Automobiles            \\ \hline
rec.motorcycles          & Category:Motorcycles            \\ \hline
rec.sport.baseball       & Category:Baseball               \\ \hline
rec.sport.hockey         & Category:Hockey                 \\ \hline
sci.crypt                & Category:Cryptography           \\ \hline
sci.electronics          & Category:Electronics            \\ \hline
sci.med                  & Category:Medicine               \\ \hline
sci.space                & Category:Outer space            \\ \hline
misc.forsale             & Category:Sales                  \\ \hline
talk.politics.misc       & Category:Politics               \\ \hline
talk.politics.guns       & Category:Gun politics          \\ \hline
talk.politics.mideast    & Category:Middle East           \\ \hline
talk.religion.misc       & Category:Religion               \\ \hline
alt.atheism              & Category:Atheism                \\ \hline
soc.religion.christian   & Category:Christians             \\ \hline
\end{tabular}
\end{table}

\begin{figure}
        \centering
        \includegraphics[height=4.0cm]{img/pmi.pdf}
        \caption{The quality of all twitter topics learned by NS-Prior-LDA increases with normal states weight (\(\lambda\)) before \(\lambda=12.8\). The optimized PMI is gained with moderate normal states weight when considering topics \(k\leq K_{\bm{KB}}\) and topics \(k > K_{\bm{KB}}\) together.}
\end{figure}
